Mean Squared Error (MSE)

\begin{equation}
    \text{MSE} = \frac{1}{n} \sum_{i=1}^{n} (y_i - \hat{y}_i)^2
\end{equation}

Penalizes large errors more than small ones due to squaring, making it useful for detecting significant deviations.
Sensitive to outliers, which can dominate the error measure.

Root Mean Squared Error (RMSE)

\begin{equation}
    \text{RMSE} = \sqrt{\frac{1}{n} \sum_{i=1}^{n} (y_i - \hat{y}_i)^2}
\end{equation}

Maintains the same unit as the target variable, making it more interpretable than MSE.
Still sensitive to outliers due to squaring before averaging.

Mean Absolute Error (MAE)

\begin{equation}
    \text{MAE} = \frac{1}{n} \sum_{i=1}^{n} |y_i - \hat{y}_i|
\end{equation}

Less sensitive to outliers than MSE and RMSE.
Does not differentiate between small and large errors as effectively as squared errors.

Mean Absolute Scaled Error (MASE)

\begin{equation}
    \text{MASE} = \frac{\frac{1}{n} \sum_{i=1}^{n} |y_i - \hat{y}_i|}{\frac{1}{n} \sum_{i=2}^{n} |y_i - y_{i-1}|}
\end{equation}

Scale-independent, making it useful for comparing forecast errors across different datasets.
Requires a meaningful benchmark (like a naive forecast) to be interpreted correctly.

Symmetric Mean Absolute Percentage Error (SMAPE)

\begin{equation}
    \text{SMAPE} = \frac{2}{n} \sum_{i=1}^{n} \frac{|y_i - \hat{y}_i|}{|y_i| + |\hat{y}_i|}
\end{equation}

Bounded between 0 and 200\%, preventing extreme values.
Can be unstable when the denominator is close to zero, leading to high error values.
